Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers

### 2023-11-04 paper/paper.tex
paper: Highlight goals of the case study earlier

In the past years, the Nix package manager\cite{Dolstra_2004} and NixOS\cite{Dolstra_2010}, a Linux distribution built around it, have emerged as promising solutions to address these challenges.
This paper explores the use of Nix/NixOS to improve the reproducibility of scientific software, focusing on a case study of preCICE\cite{preCICEv2} and its adapters and solvers.

@@

@@

\section{Nix on HPC}

@@

>>>>

In the past years, the Nix package manager\cite{Dolstra_2004} and NixOS\cite{Dolstra_2010}, a Linux distribution built around it, have emerged as promising solutions to address these challenges.
This paper explores the use of Nix/NixOS to improve the reproducibility of scientific software.

Conducting a large scale research on building scientific codes reproducibly is quite infeasible due to how many different software there is.
Therefore, we conduct a case study, focusing on preCICE\cite{preCICEv2}, its adapters and solvers.
One of the goals of the case study is to get a first hand experience and estimate on the complexity and possible challenges when packaging scientific software.
Also, consistent portability of building the software on three different systems is verified.

@@

With Nix' dependency management, we can easily copy the package definitions we just wrote onto different systems, e.g., entirely different Linux distributions, and execute the build of the closures there.
Building the same closures yields the same outputs, this will also be described in section \ref{sec:nix-on-hpc}.

@@

\section{Nix on HPC}\label{sec:nix-on-hpc}

@@

After installing Nix on HPC, we were able to produce the same binary output for the adapters and solvers as we built on our local machines as well as within the preCICE VM\footnote{The sha256 hashes of the resulting outputs were compared and matched.}
